\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of sun-like stars \vspace{-0.5cm}

### 2017-06-27 paper/ms.tex
Add lithium remark and refs

% coevality based on stellar parameters
% TODO reference supplement discussion on age here?
Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, and
\elemH{Si} in order to interpolate the age, mass, and radius of each star
using a grid of (Yale-Yonsei) model isochrones\cite{2013ApJ...776...87S}.
The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
consistent with them being coeval (see \figname~\ref{fig:yyisofitting}).

@@

We interpret the \Tcondens-dependent metal enhancement of \bizarreone\ relative
to \sunanalog\ and the very high surface \elem{Li} abundance ($A(\elem{Li}) =
2.75$) of \bizarreone\ as evidence for accretion of rocky (refractory-rich)
planetary material in \bizarreone.
In a multi-planet system, dynamical instabilities triggered by planet-planet
scattering\cite{TODO} or encounters with a field star\cite{Malmberg:2011aa} can
lead to planet ejection or accretion.
If one of the two stars in a wide binary accreted more refractory-rich (rocky) planets
than the other, this may imprint a strong \Tcondens-dependent
abundance differences like those observed in \bizarreone-\sunanalog.

@@

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars, yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium in the star's surface.
For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex
(see inset of \figname~\ref{fig:deltaxh_tcrank}).
Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
stellar parameters) very close to the Sun ($\sim 4$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $15$~\mearth\ by \bizarreone\ is consistent with a $1.65$~dex
enhancement in \elem{Li} abundance.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
approximately $1.7$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
Furthermore, this implies that the accretion event should have happened
recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).

@@

\section{Acknowledgements}
We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
for feedback.
The Flatiron Institute is supported by the Simons Foundation.
% Gaia
This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.
% software
%\software{
%  %The data and code used in this project is available from
%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
%  %software license.
%  This research utilized:
%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
%  \texttt{IPython} (\citealt{Perez:2007}),
%  \texttt{matplotlib} (\citealt{Hunter:2007}),
%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
%  and \texttt{pandas} (\citealt{pandas}).}

>>>>

% coevality based on stellar parameters
Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, and
\elemH{Si} in order to interpolate the age, mass, and radius of each star
using a grid of (Yale-Yonsei) model isochrones\cite{2013ApJ...776...87S}.
The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
consistent with them being coeval (see \figname~\ref{fig:yyisofitting}).

@@

We interpret the \Tcondens-dependent metal enhancement of \bizarreone\ relative
to \sunanalog\ and the very high surface \elem{Li} abundance ($A(\elem{Li}) =
2.75$) of \bizarreone\ as evidence for accretion of rocky (refractory-rich)
planetary material in \bizarreone.
In a multi-planet system, dynamical instabilities triggered by planet-planet
scattering\cite{1996Sci...274..954R,1996Natur.384..619W} or encounters with a
field star\cite{Malmberg:2011aa} can lead to planet ejection or accretion.
If one of the two stars in a wide binary accreted more refractory-rich (rocky) planets
than the other, this may imprint a strong \Tcondens-dependent
abundance differences like those observed in \bizarreone-\sunanalog.

@@

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars, yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium in the star's surface.
For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex
(see inset of \figname~\ref{fig:deltaxh_tcrank}).
Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
stellar parameters) very close to the Sun ($\sim 4$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $15$~\mearth\ by \bizarreone\ is consistent with a $1.65$~dex
enhancement in \elem{Li} abundance.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
approximately $1.7$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
Furthermore, this implies that the accretion event should have happened
recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).
Finally, while the current analysis of \elem{Li} line assumed a solar ratio of
$^{6}\elem{Li}/^{7}\elem{Li}$ given the data, we predict that higher resolution
spectrum of the star will reveal a significant $^{6}\elem{Li}$ which are
normally destroyed early in solar-type stars, but present in rocky
planets\cite{Israelian:2001}.

@@

\section{Acknowledgements}
We thank Andy Casey for bringing $^{6}\elem{Li}$ into our attention.
We thank Megan Bedell, Andy Casey, Keith Hawkins, Nathan Leigh, and Josh Winn
for their valuable feedback.
The Flatiron Institute is supported by the Simons Foundation.
% Gaia
This work has made use of data from the European Space Agency (ESA) mission
{\it Gaia} (\url{http://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
Data Processing and Analysis Consortium (DPAC,
\url{http://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
has been provided by national institutions, in particular the institutions
participating in the {\it Gaia} Multilateral Agreement.
% software
%\software{
%  %The data and code used in this project is available from
%  %\url{https://github.com/smoh/KronosKrios} under the MIT open-source
%  %software license.
%  This research utilized:
%  \texttt{Astropy} (\citealt{Astropy-Collaboration:2013}),
%  \texttt{emcee} (\citealt{2013PASP..125..306F}),
%  \texttt{IPython} (\citealt{Perez:2007}),
%  \texttt{matplotlib} (\citealt{Hunter:2007}),
%  \texttt{numpy} (\citealt{Van-der-Walt:2011}),
%  and \texttt{pandas} (\citealt{pandas}).}
